\documentclass{article}


%Essentials and Formatting
\usepackage[utf8]{inputenc}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{xparse}
\usepackage[margin=1in]{geometry}
\usepackage[parfill=0pt]{parskip} % Remove paragraph indentation
\usepackage{titlesec}
\usepackage{bold-extra}
\pagestyle{empty}


%Math and Science
%\usepackage{bbm}
%\usepackage{amsmath}
%\usepackage{siunitx}
%\usepackage{diffcoeff}
%\usepackage[version=4]{mhchem}


%Plotting
%\usepackage{tikz}
%\usepackage{pgfplots}
%\usepackage{pgfplotstable}
%\usepackage{csvsimple}
%\usepackage{circuitikz}


%Package configuration
\PassOptionsToPackage{colorlinks=true, allcolors=blue}{hyperref}
%\titleformat{\section}[hang]{\bfseries\scshape}{\thesection}{2ex}{}[]
%\sisetup{per-mode = fraction, list-final-separator = {, and }, group-digits=integer}
%\pgfplotsset{compat=1.18}

\newcommand{\BigSmallCaps}[2]{
    \textbf{#1}\bfseries\scshape{#2}
}

\newcommand{\rSection}[2]{
    \section*{\textbf{#1}\bfseries\scshape{#2}}\hrule
}

\begin{document}
\begin{center}
    \Huge
    \textbf{\BigSmallCaps{J}{oseph} \BigSmallCaps{T}{emple}}
    \vspace{1mm}

    \large
    \textbf{jtemple2@atu.edu \quad josepht0615@gmail.com \quad (501) 581-2301}
    \vspace{3mm}
\end{center}

\rSection{P}{rofile}
Ambitious second-year undergraduate physics student pursuing an academic career in the physical sciences. Research interests include 
theoretical and computational biophysics, acoustics, and complex systems. Key strengths include efficient balancing of several 
responsibilities and an intrinsic motivation to learn.

\rSection{E}{ducation}

\textbf{Arkansas Tech University} \hfill Russellville, AR

\vspace{-2mm}
\emph{B.S. in Physics with minor in Mathematics, B.A. in Music $\vert$ GPA: $4.0$ \hfill Expected 2026}


\rSection{E}{xperience}
\textbf{ATU Physics Department}

\vspace{-2mm}
\emph{Independent Study \hfill Jan. 2024 - Present}

\begin{itemize}
    \item Explored wave equation solutions to something something math math math.
\end{itemize}


\vspace{2mm}
\emph{Teaching Assistant for Physics 1 Lab \hfill Aug. 2023 - Dec. 2023}

\begin{itemize}
    \item Graded assignments and lab reports, providing constructive feedback to help students improve 
    their understanding of physical principles.
    \item Guided student peers through difficulties encountered in introductory mechanics experiments.
\end{itemize}

\rSection{A}{ctivities}
%\textbf{ATU Physics Department}


%\vspace{3mm}

\textbf{ATU Physics Club} %\hfill Aug. 2022 - May 2024

\vspace{-2mm}
\emph{Vice President \hfill Aug. 2023 - Present}

\begin{itemize}
    \item Facilitated discussions to generate ideas for club events, projects, and outreach initiatives.
    \item Showcased physical demonstrations to inspire interest in science among the wider campus community.
\end{itemize}



\rSection{T}{echnical Skills}

\begin{itemize}
    \item Object-oriented programming in C\texttt{++}. (Intermediate)
    \item Numerical computing in Python using \verb|numpy|, \verb|matplotlib|, and \verb|scipy|. (Beginner)
    \item Proficiency with \LaTeX \ using \verb|tikz|, \verb|pgfplots|, \verb|csvsimple|, etc.
\end{itemize}




\rSection{R}{eferences}
\textbf{Dr. Jessica Young}, Associate Professor of Physics \hfill \verb|jyoung35@atu.edu|

\textbf{Dr. Jon Clements}, Professor of Music \hfill \verb|jclements@atu.edu|

\textbf{Dr. Matthew Hankins}, Assistant Professor of Physics \hfill \verb|mhankins1@atu.edu|

\end{document}